Evidence accumulation for tackling research waste

### 2020-01-28 Manuscript/MS.Rmd
update 27.01.2020
ggsave path changed

#ggsave("C:/Users/matthew.grainger/OneDrive - NINA/Papers_in_prep/Cumulative_meta_analysis/Research_waste/Figures/Fig1._Cumulative_Forest.png", p, device = "png")

>>>>

#ggsave("C:/Users/matthew.grainger/OneDrive - NINA/Papers_in_prep/Cumulative_meta_analysis/Research_waste/Figures/Fig1._Cumulative_Forest.pdf", p, device = "pdf")
